### 2020-04-29 Paper_EV/Paper_EV.tex
Submission on 22_04_2020

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
% TODO:
% - Change date on the title page
% - Change date on the statutory declaration page
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

@@

% For some reason fisrt chapter has a different vert. spacing from the top, so we add additional 0.8cm, starred command makes sure it will not be suppressed at the beginning or at the end of the page
\vspace*{-0.8cm}
\section*{Statutory Declaration}
I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universität München, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
\\
\\
This thesis has neither as-is nor similarly been submitted to any other university.
\bigskip
\\
\\
Garching, April 25, 2020
\\
\\
\\
\\
Evghenii Volodscoi

@@

\section*{Kurzfassung} \label{sec:kurzfassung}
% Start cursive block
\begin{itshape}
Inkrementelle Nichtlineare Dynamische Inversion (INDI) is ein vielversprechender Reglertyp, welcher h\"aufig f\"ur die Regelung von nichtlinearen Flugsystemen unterschiedlicher Art eingesetzt wird. Ein Vorteil der INDI ist, dass dieser Reglertyp kein detalliertes Modell der geregelten Strecke ben\"otigt. Au\ss{}erdem, wirkt INDI sehr effektiv gegen St\"orungen. Diese Semesterarbeit befasst sich mit der Auslegung eines INDI-Reglers f\"ur die Lage- und Positionsregelung eines Nano-Quadrotors. Die Arbeit beginnt mit der Herleitung des Regelalgorithmus. Der hergeleitete Regelgesetz wird dann erst in Simulink entwickelt und anschlie\ss{}end auf der Quadrotor-Hardware implementiert. Dazu werden solche Implementierungsaspekte wie Ermittlung der Eingangsmatrix, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen. Abschlie\ss{}end, wird der implementierte Regler auf die F\"ahigkeit St\"orungen zu bek\"ampfen getestet. Der finale Regler ist \"uber das offizielle Open-Source-Firmware des Crazyflie-Quadrotors verf\"ugbar. 
\end{itshape}

@@

The transfer function of the first order lag element (Equation \ref{eq:act_dynamics_c}) in time domain has the following form 
\begin{equation}
	a(t) = 	k (1 - e^{\frac{-t}{T}})
	\label{eq:act_dynamics_time}
\end{equation}
The fitting is then done by minimizing the squared error between measured $a_{measured}$ and predicted $a$ data. For multiple measurements in discrete time steps the objective function $E(T)$ is defined as 
\begin{equation}
	E(T) = \sum_{t}^{} (a(T) - a_{measured}(T))^2
	\label{eq:obj_function}
\end{equation}
$T$ is then computed using the least squares approach such that Equation \ref{eq:obj_function} is minimal. Note that in Equation \ref{eq:obj_function} $a(T)$ is a function of the time constant $T$, since it is an optimization parameter. Figure \ref{fig:actuator_dynamics_est} shows the obtained result of the optimization. Here, the red curve was fitted to the measured data (blue line). In the figure the signal contains $n=155$ samples recorded with a frequency of $200~\si{\Hz}$. The estimated value for the time constant is $T = 0.061658 \ s$.

>>>>

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

% Package for adding table of contents and references to the generated pdf document
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, allcolors=black}

@@

% For some reason fisrt chapter has a different vert. spacing from the top, so we add additional 0.8cm, starred command makes sure it will not be suppressed at the beginning or at the end of the page
\vspace*{-0.8cm}
\section*{Statutory Declaration}
I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universit\"at M\"unchen, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
\\
\\
This thesis has neither as-is nor similarly been submitted to any other university.
\bigskip
\\
\\
Garching, April 22, 2020
\\
\\
\\
\\
Evghenii Volodscoi

\includegraphics[scale=0.35]{figs/signatur.jpg}\par

@@

\section*{Kurzfassung} \label{sec:kurzfassung}
% Start cursive block
\begin{itshape}
Inkrementelle Nichtlineare Dynamische Inversion (INDI) is ein vielversprechender Reglertyp, welcher h\"aufig f\"ur die Regelung von nichtlinearen Flugsystemen unterschiedlicher Art eingesetzt wird. Ein Vorteil der INDI ist, dass kein detalliertes Modell der geregelten Strecke ben\"otigt wird. Au\ss{}erdem, wirkt INDI sehr effektiv gegen St\"orungen. Diese Semesterarbeit befasst sich mit der Auslegung eines INDI-Reglers f\"ur die Lage- und Positionsregelung eines Nano-Quadrotors. Die Arbeit beginnt mit der Herleitung des Regelalgorithmus. Das hergeleitete Regelgesetz wird dann erst in Simulink entwickelt und anschlie\ss{}end auf der Quadrotor-Hardware implementiert. Dazu werden solche Implementierungsaspekte wie die Ermittlung der Eingangsmatrix, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen. Abschlie\ss{}end, wird der implementierte Regler auf die F\"ahigkeit St\"orungen zu unterdr\"ucken getestet. Der finale Regler ist \"uber das offizielle Open-Source-Firmware des Crazyflie-Quadrotors verf\"ugbar. 
\end{itshape}

@@

The transfer function of the first order lag element (Equation \ref{eq:act_dynamics_c}) in time domain has the following form 
\begin{equation}
	a(t) = 	k (1 - e^{\frac{-t}{T}})
	\label{eq:act_dynamics_time}
\end{equation}
The fitting is then done by minimizing the squared error between measured $a_{measured}$ and predicted $a$ data. For multiple measurements in discrete time steps the objective function $E(T)$ is defined as 
\begin{equation}
	E(T) = \sum_{t}^{} (a(T) - a_{measured}(T))^2
	\label{eq:obj_function}
\end{equation}
$T$ is then computed using the least squares approach such that Equation \ref{eq:obj_function} is minimal. Note that in Equation \ref{eq:obj_function} $a(T)$ is a function of the time constant $T$, since it is an optimization parameter. Figure \ref{fig:actuator_dynamics_est} shows the obtained result of the optimization. Here, the red curve was fitted to the measured data (blue line). In the figure the signal contains $n=155$ samples recorded with a frequency of $200~\si{\Hz}$. The estimated value for the time constant is $T = 0.061658~\si{\s}$.

### 2020-04-29 temp/version_for_plagiarism_check/Paper_EV.tex
Submission on 22_04_2020

% Set style for pages with arabic numbering 
% This block prints only the chapter number and the chapter name, not the word "Chapter"
%\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
% Clear current page style 
\fancyhf{}
% Head (11 pt font size and 12 pt line spacing)
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}
% Foot (11 pt font size and 12 pt line spacing)
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{pagesLTS.arabic}}
% Line settings
\renewcommand{\headrulewidth}{0.1pt}	%upper line
\renewcommand{\footrulewidth}{0.1pt}	%lower line

% Set style for pages with roman numbering 
\fancypagestyle{fancy_beginning}{%
%\pagestyle{fancy}
% Clear current page style 
\fancyhf{}%
% Head
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}%
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}%
% Foot
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}%
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage}%
% Line settings
\renewcommand{\headrulewidth}{0.1pt}%	%upper line
\renewcommand{\footrulewidth}{0.1pt}%	%lower line
}

@@

% For some reason fisrt chapter has a different vert. spacing from the top, so we add additional 0.8cm, starred command makes sure it will not be suppressed at the beginning or at the end of the page
\vspace*{-0.8cm}
\section*{Statutory Declaration}
I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universit\"at M\"unchen, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
\\
\\
This thesis has neither as-is nor similarly been submitted to any other university.
\bigskip
\\
\\
Garching, April 22, 2020
\\
\\
\\
\\
Evghenii Volodscoi

\includegraphics[scale=0.35]{figs/signatur.jpg}\par

>>>>

% Set style for pages with arabic numbering 
% This block prints only the chapter number and the chapter name, not the word "Chapter"
%\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
% Clear current page style 
\fancyhf{}
% Head (11 pt font size and 12 pt line spacing)
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}
% Foot (11 pt font size and 12 pt line spacing)
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}--- ---}
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{pagesLTS.arabic}}
% Line settings
\renewcommand{\headrulewidth}{0.1pt}	%upper line
\renewcommand{\footrulewidth}{0.1pt}	%lower line

% Set style for pages with roman numbering 
\fancypagestyle{fancy_beginning}{%
%\pagestyle{fancy}
% Clear current page style 
\fancyhf{}%
% Head
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}%
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}%
% Foot
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}--- ---}%
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage}%
% Line settings
\renewcommand{\headrulewidth}{0.1pt}%	%upper line
\renewcommand{\footrulewidth}{0.1pt}%	%lower line
}

@@

% For some reason fisrt chapter has a different vert. spacing from the top, so we add additional 0.8cm, starred command makes sure it will not be suppressed at the beginning or at the end of the page
\vspace*{-0.8cm}
\section*{Statutory Declaration}
I, --- ---, declare on oath towards the Institute of Flight System Dynamics of Technische Universit\"at M\"unchen, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
\\
\\
This thesis has neither as-is nor similarly been submitted to any other university.
\bigskip
\\
\\
Garching, April 22, 2020
\\
\\
\\
\\
--- ---
